Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm

### 2024-08-24 paper/main.tex
Progress in explaining the simulation

\section{MATLAB Simulation of the Receiver}
To verify and underline the working principle of the receiver, a simulation of the whole system was created using MATLAB.
The whole simulation was divided into five sections to allow for a clear structure:
\begin{enumerate}
    \item Simulation Parameter Section
    \item Signal Creation Section
    \item Goertzel Algorithm Section
    \item Detection Section
    \item FFT and Plot Section
\end{enumerate}
These sections will be discussed in the following.

\subsection{Simulation Parameter Section}
In the Simulation Parameter Section, static parameters for the following sections are defined.
These include the sampling frequency $f_{s}$, the duration of the whole simulation, the wanted SNR that the signal should have after passing the Additive White Gaussian Noise (AWGN)-Channel, the duration of the Goertzel algorithm segments, and the time that should
be taken into account by the EMA.
By adjusting these parameters, the behavior of the receiver can be altered to, e.g. to simulate different receiving conditions.

\subsection{Signal Creation Section}

>>>>

\section{Simulation of the receiver in MATLAB}
To verify and further explain the working principle of the receiver, a simulation of the whole system was created using MATLAB.
The whole simulation was divided into five sections to allow for a clear structure:
\begin{enumerate}
    \item Simulation Parameter Section
    \item Signal Creation Section
    \item Goertzel Algorithm Section
    \item Detection Section
    \item FFT and Plot Section
\end{enumerate}
These sections will be discussed in the following.

\subsection{Simulation Parameter Section}
In the Simulation Parameter Section, static parameters for the following sections of the simulation are defined.
These include the sampling frequency $f_{s}$, the duration of the whole simulation, the SNR that the signal should have after passing the Additive White Gaussian Noise (AWGN)-Channel, the frequency to be analyzed by the Goertzel algoritm, the duration of the Goertzel algorithm segments, and the time that should be taken into account by the EMA.
By adjusting these parameters, the receiving situation and the receiver's behavior can be altered to, e.g. to simulate different receiving conditions and examine the system's performance.

\subsection{Signal Creation Section}
The Signal Creation Section implements the creation of the amplitude-modulated DCF77 signal.
First, a time vector with the length of the simulation's duration and a step size that depends on $f_{s}$ is created and its length stored in a variable.
A vector containing the carrier signal at $f_{c} = \SI{77.5}{\kilo\hertz}$ by using this time vector is created afterwards.
For the amplitude modulation of the carrier, the time code signal containing the binary encoded symbols needs to be created.
As this signal is used for multiplication with the carrier, it needs to consist of rects with a period length of \SI{1}{\second} and a gap of either \SI{200}{\milli\second} or \SI{100}{\milli\second} at the beginning.
These rects are prepared by creating and filling two vectors with the matching amount of zeros followed and filling the rest with ones.
A vector containing the time code signal with alternating symbols is created by concatenating these vectors inside a for loop.
The number of iterations is given by rounding up the simulation's duration, because each symbol has the duration of \SI{1}{\second}.
The vector is then cut down afterwards to exactly match the length of the time vector and therefore the duration of the simulation.
To finally create the DCF77 signal, the vector with the time code signal is scaled and multiplied element-wise with the vector containing the carrier signal.
This signal is then passed through a AWGN-Channel, creating a signal with a defined SNR to allow the simulation of different receiving conditions.

\subsection{Goertzel Algorithm Section}
